TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
still plotting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
```

@@

```{r}
# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                      median, data = all_vas)
vas_h1 <- aggregate(VAS)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_grid(~quality*manipulation) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
library(tidyverse)
library(gghalves)
library(ggpol)
```

@@

```{r}
# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*condition*cold_probe*ID, 
                      median, data = all_vas)
vas_h1 <- aggregate(VAS ~ quality*manipulation*condition*ID, mean, data = vas_meds)

# summary means for h1

# then plot :D
# first colours
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")
purp <- brewer.pal(6, "Purples")
oran <- brewer.pal(6, "Oranges")
gren <- brewer.pal(6, "Greens")

# nudge and jitter
nudge1 = -0.1
nudge2 = 0.1
vas_h1$dermatome <- ifelse(vas_h1$condition == 'within', 1, 2)  # recode within and across
vas_h1$condition <- factor(vas_h1$condition, labels = c('within', 'across'),
                           levels = c('within', 'across'))
# recode quality for this plot
vas_h1$quality1[vas_h1$quality == 'cold'] <- 1
vas_h1$quality1[vas_h1$quality == 'warm'] <- 2
vas_h1$quality1[vas_h1$quality == 'burn'] <- 3

vas_h1$xj <- jitter(vas_h1$quality1, 0.2)

ggplot(data = vas_h1, aes(colour = condition, group = ID)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(purp[6], purp[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  theme_classic() -> h1_cnt_plot

ggplot(data = vas_h1, aes(colour = condition)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(purp[6], purp[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  theme_classic() -> h1_tgi_plot

h1_plot <- ggarrange(h1_cnt_plot, h1_tgi_plot,
                     ncol = 2, nrow = 1,
                     common.legend = TRUE)
h1_plot
```

@@

# ZOIB regression
Running main analysis of a zero inflated beta regression
Outcome: VAS
Predictors: manipulation (CNT, TGI), cold probe location ()
Run a seperate regression for each quality
# Cold
# Warm
# Burn

# Run one regression including quality as a predictor
